Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-05 Ben_Manuscripts/structure_paper/supplemental.tex
10 dbwl updated

>>>>

	  Figure ~\ref{fig:dbwl_10} shows the structure of an assembly built
	  with an initial layer spacing of 10 \AA immediately after the restrained
	  portion of the equilibration procedure. Since position restraints, the
	  simulations are run in the NVT ensemble. When layer spacing is large, such as
	  this situation, there is a significant amount of vacuum space which the monomer
	  attempts to fill.  Even if turning pressure control on allows the system to
	  recover the geometry of the hexagonal phase, we would likely need much longer
	  equilibration times, and it will almost certainly remain trapped in metastable
	  configurations that bear no resemblence to experimental profiles.

	  \begin{figure}
		\centering
		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
		\caption{}\label{fig:dbwl_10} 
	  \end{figure}
